Manuscript draft

### 2019-06-24 manuscript/manuscript draft.Rmd
updated manuscript draft

---
title: "Manuscript draft"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: library.bib
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}

@@

>>>>

---
title: "Manuscript draft"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}

@@

```{r include=FALSE}
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'lme4', 'MuMIn', 'plyr', 'raster', 'ncdf4', 'Hmisc', 'plyr', 'merTools', 'visreg', 'r2glmm', 'nlme', 'viridis', 'ggplot2', 'ggpubr', 'gridExtra'
), 'packages.bib')
```
